Exploration

### 2018-03-05 exploration.Rmd
vectorized dispersal calculations

## Simulation: IPM framework
```{r S}
########
## set up
########
# set up storage & IPM matrix objects
p <- sp_i$p
setup_IPM_matrix(n, z.rng, buffer=0.25, discrete=1)
IPMs <- Ps <- Fs <- array(0, dim=c(n+1, n+1, n.cell))
d <- vector("list", length=n.cell)
B <- rpois(n.cell, n_i)
B_1 <- nSd <- D <- rep(NA, n.cell)
sdd <- array(0, dim=dim(sdd.pr) + c(0,0,1,0)) # add layer for nEmig
sdd[,,1:2,] <- sdd.pr

@@

  #---- Truth: use assigned slopes to fill IPM matrix
  ### growth and survival
  G.mx <- h*outer(y, y, calc_grow, p=p, n_gz=n_gz, X.g=X_g[i,])
  S.v <- calc_surv(y, p=p, n_sz=n_sz, X.s=X_s[i,])
  ### Fix eviction of individuals below/above size limits
  for(k in 1:(n/2)) G.mx[1,k] <- G.mx[1,k] + 1 - sum(G.mx[,k])
  for(k in (n/2+1):n) G.mx[n,k] <- G.mx[n,k] + 1 - sum(G.mx[,k])
  ### fill P and F matrices
  for(k in z.i) Ps[k,z.i,i] <- G.mx[k-1,]*S.v
  Ps[1,1,i] <- calc_staySB(p)
  Fs[z.i,z.i,i] <- h*outer(y, y, calc_rcrDir, p=p, n_seedz=n_seedz,
                             n_flz=n_flz, X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fs[1,z.i,i] <- calc_DirSB(y, p=p, n_seedz=n_seedz, n_flz=n_flz, 
                            X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fs[z.i,1,i] <- calc_rcrSB(y, p)

@@

  #---- Truth: add immigrants
  sdd.j <- which(sdd[,,2,]==sdd.i, arr.ind=TRUE)[,3]
  p.ij <- sdd[,,1,sdd.j][sdd[,,2,sdd.j]==sdd.i]
  imm.rcr <- map2(sdd.j, p.ij, 
                     ~h*outer(y, y, calc_rcrImm, p=p, .y, n_seedz=n_seedz,
                              n_flz=n_flz, X.seed=X_seed[.x,], X.fl=X_fl[.x,]))
  Fs[z.i,z.i,i] <- Fs[z.i,z.i,i] + Reduce(`+`, imm.rcr)
  imm.sb <- map2(sdd.j, p.ij,
                     ~calc_ImmSB(y, p=p, .y, n_seedz=n_seedz, n_flz=n_flz,
                                 X.seed=X_seed[.x,], X.fl=X_fl[.x,]))
  Fs[1,z.i,i] <- Fs[1,z.i,i] + 
    Reduce(`+`, imm.sb)

>>>>

## Simulation: IPM framework
```{r S}
########
## set up
########
# set up storage & IPM matrix objects
p <- sp_i$p
setup_IPM_matrix(n, z.rng, buffer=0.25, discrete=1)
IPMs <- Ps <- Fs <- Fb <- array(0, dim=c(n+1, n+1, n.cell))
d <- vector("list", length=n.cell)
B <- rpois(n.cell, n_i)
B_1 <- nSd <- D <- rep(NA, n.cell)
sdd <- array(0, dim=dim(sdd.pr) + c(0,0,1,0)) # add layer for nEmig
sdd[,,1:2,] <- sdd.pr

@@

  #---- Truth: use assigned slopes to fill IPM matrix
  ### growth and survival
  G.mx <- h*outer(y, y, calc_grow, p=p, n_gz=n_gz, X.g=X_g[i,])
  S.v <- calc_surv(y, p=p, n_sz=n_sz, X.s=X_s[i,])
  ### Fix eviction of individuals below/above size limits
  for(k in 1:(n/2)) G.mx[1,k] <- G.mx[1,k] + 1 - sum(G.mx[,k])
  for(k in (n/2+1):n) G.mx[n,k] <- G.mx[n,k] + 1 - sum(G.mx[,k])
  ### fill P and F matrices
  for(k in z.i) Ps[k,z.i,i] <- G.mx[k-1,]*S.v
  Ps[1,1,i] <- calc_staySB(p)
  ### store seed production
  Fb[z.i,z.i,i] <- outer(y, y, calc_rcrDir, p=p, n_seedz=n_seedz, n_flz=n_flz, 
                         X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fb[1,z.i,i] <- calc_addSB(y, p=p, n_seedz=n_seedz, n_flz=n_flz, 
                            X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fs[z.i,z.i,i] <- h * (1 - p$p_emig) * Fb[z.i,z.i,i]
  Fs[1,z.i,i] <- (1 - p$p_emig) * Fb[1,z.i,i]
  Fs[z.i,1,i] <- calc_rcrSB(y, p)

@@

  #---- Truth: add immigrants
  sdd.j <- which(sdd[,,2,]==sdd.i, arr.ind=TRUE)[,3]
  p.ij <- sdd[,,1,sdd.j][sdd[,,2,sdd.j]==sdd.i]
  Fs[z.i,z.i,i] <- Fs[z.i,z.i,i] + 
    Reduce(`+`, map2(sdd.j, p$p_emig*p.ij, ~(Fb[z.i,z.i,.x] * .y)))
  Fs[1,z.i,i] <- Fs[1,z.i,i] + Fb[1,z.i,sdd.j] %*% (p$p_emig*p.ij)
